---
output:
  md_document;
  github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

`"binomial"` is a package that provides functions for binomial calculations

* `bin_variable()` creates a binomial variable object (of class `"coin"`)
* `bin_choose()` simulates a choose problem and calculates the number of different outcomes.
* `bin_probability()` calculates the probability of a binomial distribution.
* `bin_distribution()` calculates the probability of a binomial distribution and displays them in a list.
* `bin_cumulative()` calculates the probability of a cumulative binomial distribution and displays them in a list.
* `bin_mean()` computes the expected mean of a binomial distribution.
* `bin_variance()` computes the expected variance of a binomial distribution.
* `bin_mode()` computes the expected mode of a binomial distribution.
* `bin_skewness()` computes the expected skewness of a binomial distribution.
* `bin_kurtosis()` computes the expected kurtosis of a binomial distribution.
* `print()` method for a `"binvar"` object.
* `print()` method for a `"bindis"` object.
* `print()` method for a `"bincum"` object.
* `print()` method for a `"summary.binvar"` object.
* `summary()` method for a `"binvar"` object.
* `plot()` method for a `"bindis"` object.
* `plot()` method for a `"bincum"` object.


## Motivation

This package has been developed to illustrate some of the concepts
behind the creation of an R package.


## Usage

```{r}
library(binomial)
mybinvar <- bin_variable(trials = 10, prob = 0.5)
mybinvar

mybinvar <- bin_variable(trials = 10, prob = 0.5)
summary_binvar <- summary(mybinvar)
summary_binvar

bin_choose(n = 5, k = 3)

bin_distribution(trials = 10, prob = 0.5)

bin_cumulative(trials = 10, prob = 0.5)

bin_dis <- bin_distribution(trials = 5, prob = 0.5)
plot(bin_dis)

bin_cum <- bin_cumulative(trials = 5, prob = 0.5)
plot(bin_cum)

bin_mean(trials = 10, prob = 0.5)

bin_skewness(trials = 10, prob = 0.5)
```
